New lower bounds for Schur and weak Schur numbers

### 2021-04-09 article/weakschur.tex
lemme+tableau

\subsection{Definition of \(WS^+\)}
\begin{definition}
Let \( (p,k,b) \in (\mathbb{N}^*)^3\), Let \((A_1,....,A_k)\) a partition of  \([\![1, p]\!]\).
This partition is said to be a b-weakly-sum-free template (b-WSF-template) of \(k\) colors and lenght \(p\) when:
\\\\
\underline{\(\forall i \in [\![1, k]\!], \quad A_i\) is weakly-sum-free}
\\\\
\underline{\(\forall i \in [\![1, k]\!], \quad A_i\backslash [\![1, b]\!]\) is sum-free}
\\\\
\underline{For \(A_k\) (the special subset):} \quad \(\forall (x,y) \in A_k^2,\)
\\
\[if \quad x+y>b+2(p-b),\quad x+y-2(p-b)\notin A_k\]
\\
\underline{For the others subsets:}\quad \(\forall i \in [\![0,k-1]\!], \forall(x,y) \in A_i^2\)
\\
\[
(Id+(p-b)\mathbf{1}_{ [\![0,b]\!]})(x+y ~\text{mod}~ (p-b)) \notin A_i
\]
\end{definition}

@@

>>>>

\subsection{Definition of \(WS^+\)}

We will now define notations and results, we will use in the following theorem.

\begin{notation}

Let (a,b) \(n \in (\mathbb{N}^*)^2\),\(a>b\), we will define \(\pi_{a,b}\) the projection:
\[ \pi_{a,b}:x->(Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x mod a}))\]
\end{notation}

We will note  the projection \(\pi\) and not \(\pi_{a,b}\) when there is no doubt about the a and b we use.

\begin{Proposition}
Let x \(\in [\![1,b]\!]\), let y \(\in \mathbb{N}^*\) such that \(x+\pi(y)\leqslant a+b\), then we have: \(\pi(x+y)=x+\pi(y)\)
\end{Proposition}

\textsc{Proof :}Let x \(\in [\![1,b]\!]\), let y \(\in \mathbb{N}^*\) such that \(x+\pi(y)\leqslant a+b\)

\\\\if \(x+\pi(y)< a:\)we remark that \(\pi(y)>b\) and therefore \(x+\pi(y)>b\):

\begin{align*}
 \\\pi(x+y) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x+y mod a})\\
& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y)\text{ mod a) since } \pi(y)\text{=y mod a} \\
& =x+ \pi(y)
\end{align*}

\\if \(x+\pi(y\geqslant a\):
\begin{align*}
 \\\pi(x+y) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x+y mod a})\\
& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y)\text{ mod a) since } \pi(y)\text{=y mod a} \\
& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y) - a) \\
& = x+\pi(y) - a +a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y) - a) \\
& = x+\pi(y) - a +a \text{ \quad since } x+\pi(y) - a \in [\![0,b]\!] \\
& = x+\pi(y)
\end{align*}

\begin{Proposition}
Let (x,y)\(\in (\mathbb{N}^*)^2\), \(\pi(\pi(x)+\pi(y))=\pi(x+y)\)
\end{Proposition}

\textsc{Proof :}Let (x,y)\(\in (\mathbb{N}^*)^2\),

\begin{align*}
 \\\pi(\pi(x)+\pi(y)) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\pi(x)+\pi(y)\text{ mod a})\\
& = (Id+a\mathbf{1}_{ [\![0,b]\!]})((Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x mod a})+(Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{y mod a})\text{ mod a}) \\
& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{ ((x mod a) + (y mod a)) mod a})\\
& =(Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{ x+y mod a})\\
& =\pi(x+y)
\end{align*}

\begin{notation}

Let (a,b) \(n \in (\mathbb{N}^*)^2\),\(a>b\), we will define \(\lambda_{a,b}\) the projection:
\[ \lambda_{a,b}:x->1+ \left\lfloor\dfrac{x-b-1}{a}\right\rfloor\]
\end{notation}

We will note  the projection \(\lambda\) and not \(\lambda_{a,b}\) when there is no doubt about the a and b we use.

\begin{remark}
In the following theorem, \(\lambda\) is the function which return the line number of an element x.
\end{remark}

\begin{Proposition}
Let (a,b)\(\in (\mathbb{N}^*)^2\), \(a>b\), let x \(\in \mathbb{N}^*\), \(x=a\lambda(x)+\pi(x)-a\)
\end{Proposition}
\textsc{Proof :}Let (a,b)\(\in (\mathbb{N}^*)^2\), \(a>b\), let x \(\in \mathbb{N}^*\),
\\\\ \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x-b-1}{a}\right\rfloor+(\text{x mod a})+\mathbf{1}_{ [\![0,b]\!]}(\text{x mod a})\)

\\\\if x mod a \(>b\): \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x}{a}\right\rfloor+\text{x mod a}=x\)

\\\\if x mod a \(\leqslant b\):
\(a\lambda(x)+\pi(x)-a=a(\left\lfloor\dfrac{x}{a}\right\rfloor-1)+\text{x mod a}+a=x\)
\begin{definition}
Let \( (p,k,b) \in (\mathbb{N}^*)^3\), Let \((A_1,....,A_k)\) a partition of  \([\![1, p]\!]\).
This partition is said to be a b-weakly-sum-free template (b-WSF-template) of \(k\) colors and lenght \(p\) when:
\\\\
\underline{\(\forall i \in [\![1, k]\!], \quad A_i\) is weakly-sum-free}
\\\\
\underline{\(\forall i \in [\![1, k]\!], \quad A_i\backslash [\![1, b]\!]\) is sum-free}
\\\\
\underline{For \(A_k\) (the special subset):} \quad \(\forall (x,y) \in A_k^2,\)
\\
\[if \quad x+y>b+2(p-b),\quad x+y-2(p-b)\notin A_k\]
\\
\underline{For the others subsets:}\quad \(\forall i \in [\![0,k-1]\!], \forall(x,y) \in A_i^2\)
\\
\[
(Id+(p-b)\mathbf{1}_{ [\![0,b]\!]})(x+y ~\text{mod}~ (p-b)) \notin A_i
\]
\end{definition}

@@

\renewcommand{\arraystretch}{2}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{green}} c|}
\hline
  & & & & & \cellcolor{green}1 & \cellcolor{green}2 & \cellcolor{blue} 3&\cellcolor{green}4&5&6&7&8 \\
\hline
   \cellcolor{red}9 & \cellcolor{red}10 & \cellcolor{red}11 & \cellcolor{red}12 &\cellcolor{red}13&\cellcolor{red}14&\cellcolor{red}15&\cellcolor{red}16&\cellcolor{red}17&18&19&20&21\\
\hline
\cellcolor{yellow}22&\cellcolor{yellow}23&\cellcolor{yellow}24&\cellcolor{yellow}25&\cellcolor{yellow}26&\cellcolor{yellow}27&\cellcolor{yellow}28&\cellcolor{yellow}29&\cellcolor{yellow}30&31&32&33&34\\
\hline
...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...&...&...&...\\
\hline
\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&...&...&...&...\\
\hline
...&...&...&...&...&...&...&...&...&...&...&...&...\\
\hline
\end{tabular}
